Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-17 paper.qmd
Updated Figure 12

pacmap_two_c_shaped_clust_plt <- pacmap_two_curvy_scaled |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2))+
  geom_point(alpha=0.1, size=1, colour='#e41a1c') +
  interior_annotation("b1", sc_ltr_pos) +
  theme(aspect.ratio = 1)

@@

trimesh_two_curvy_removed1_pacmap_with_data <- ggplot() +
  geom_segment(data = tr_from_to_df_two_curvy4,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  geom_point(data = pacmap_two_curvy_scaled,
             aes(
               x = PaCMAP1,
               y = PaCMAP2
             ),
             color = "#a65628",
             alpha = 0.5,
             size = 0.5) +
  coord_equal() +
  interior_annotation("b2", sc_ltr_pos)

@@

two_curvy_proj_pacmap_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") + #31a354
  geom_point(
    size = 0.5,
    alpha = 0.5,
    color = "#a65628") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.126, 0.125)) + 
  ylim(c(-0.126, 0.125)) +
  interior_annotation("b3", sc_ltr_pos) +
  theme(
    legend.position = "none"
  )

two_curvy_proj_pacmap_all_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = true_model_df_proj, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#2b8cbe") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") +
  geom_point(
    size = 0.5,
    alpha = 0.5,
    color = "#a65628") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.126, 0.125)) + 
  ylim(c(-0.126, 0.125)) +
  interior_annotation("b4", sc_ltr_pos) +
  theme(
    legend.position = "none"
  )
```

@@

nldr_two_curvy_original2 + tsne_two_c_shaped_clust_plt +
  pacmap_two_c_shaped_clust_plt +
  trimesh_two_curvy_removed1_with_data + trimesh_two_curvy_removed1_tsne_with_data +
trimesh_two_curvy_removed1_pacmap_with_data +
  two_curvy_proj_umap_model2 +
  two_curvy_proj_tsne_model +
  two_curvy_proj_pacmap_model +
  two_curvy_proj_umap_all_model +
  two_curvy_proj_tsne_all_model +
  two_curvy_proj_pacmap_all_model +
  plot_layout(ncol = 3)
```

>>>>

pacmap_two_c_shaped_clust_plt <- pacmap_two_curvy_scaled |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2))+
  geom_point(alpha=0.1, size=1, colour='#e41a1c') +
  interior_annotation("c1", sc_ltr_pos) +
  theme(aspect.ratio = 1)

@@

trimesh_two_curvy_removed1_pacmap_with_data <- ggplot() +
  geom_segment(data = tr_from_to_df_two_curvy4,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  geom_point(data = pacmap_two_curvy_scaled,
             aes(
               x = PaCMAP1,
               y = PaCMAP2
             ),
             color = "#e41a1c",
             alpha = 0.5,
             size = 0.5) +
  coord_equal() +
  interior_annotation("c2", sc_ltr_pos)

@@

two_curvy_proj_pacmap_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") + #31a354
  geom_point(
    size = 0.5,
    alpha = 0.5,
    color = "#e41a1c") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.126, 0.125)) + 
  ylim(c(-0.126, 0.125)) +
  interior_annotation("c3", sc_ltr_pos) +
  theme(
    legend.position = "none"
  )

two_curvy_proj_pacmap_all_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = true_model_df_proj, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#2b8cbe") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") +
  geom_point(
    size = 0.5,
    alpha = 0.5,
    color = "#e41a1c") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.126, 0.125)) + 
  ylim(c(-0.126, 0.125)) +
  interior_annotation("c4", sc_ltr_pos) +
  theme(
    legend.position = "none"
  )
```

@@

nldr_two_curvy_original2 + tsne_two_c_shaped_clust_plt +
  pacmap_two_c_shaped_clust_plt +
  trimesh_two_curvy_removed1_with_data + trimesh_two_curvy_removed1_tsne_with_data +
trimesh_two_curvy_removed1_pacmap_with_data +
  two_curvy_proj_umap_model2 +
  two_curvy_proj_tsne_model +
  two_curvy_proj_pacmap_model +
  two_curvy_proj_umap_all_model +
  two_curvy_proj_tsne_all_model +
  two_curvy_proj_pacmap_all_model +
  plot_layout(ncol = 3) +
  plot_annotation(tag_levels = list(c("(a)", "(b)", "(c)")))
```
